\textbf{CSDS 440 Class Project: \\Adversarial Machine Learning}

### 2020-12-05 report/article.tex
🔨 Compress photo to make them small and speed up LaTeX compile.

I have wholeheartedly lead and contributed to this group projects, below is an itemized list of my contributions. I have inquired Dr. Ray and confirmed they can be considered as ``extra works'' and maybe give me some grade boost. Thanks.
\begin{itemize}
    \item Read 3 papers on algorithms.
    \item Implemented 2 algorithms (\ilc{FGSM} and \ilc{Hop Skip Jump}) with 3 extensions.
    \item Piplined attack algorithms to work with 2 datasets, collected almost all (7 algorithms/useable extensions) attack experiments data (except \ilc{backdoor} and \ilc{one pixel attack}) for the comparative evaluations.
    \item Piplined and collected experiments data for \ilc{FGSM, Hop Skip Jump, DeepFool} attacks (and their useable extensions) against \ilc{Detector} and \ilc{Spatial Smoothing} defenses on 2 datasets.
    \item Implemented $L_2$ and $L_{\infty}$ \textit{perturbation budget} to aid comparative evaluation.
    \item Wrote \textbf{Introduction and Significance} section.
    \item Plotted all graphs and charts in \textbf{Comparative Study and Discussion}.
    \item Helped group move forward by making technical decisions, distributing works, setting up deadlines, and facilitating coordination between groupmates.
\end{itemize}

@@

\ilc{FGSM} is a \textit{white-box} evasion attack algorithm. Being \text{white-box} meaning the attacker was assumed to have access to the internal of the model,

>>>>

I have wholeheartedly lead and contributed to this group project, below is an itemized list of my contributions. I have inquired Dr. Ray and confirmed these can be considered as ``extra works'' and maybe give me some grade boost. Thanks :)
\begin{itemize}
    \item Read 3 papers on algorithms.
    \item Implemented 2 algorithms (\ilc{FGSM} and \ilc{Hop Skip Jump}) with 3 extensions.
    \item Piplined attack algorithms to work with 2 datasets, collected almost all (7 algorithms/useable extensions) attack experiments data (except \ilc{backdoor} and \ilc{one pixel attack}) for the comparative evaluations.
    \item Piplined and collected experiments data for \ilc{FGSM, Hop Skip Jump, DeepFool} attacks (and their useable extensions) against \ilc{Detector} and \ilc{Spatial Smoothing} defenses on 2 datasets.
    \item Implemented $L_2$ and $L_{\infty}$ \textit{perturbation budget} to aid comparative evaluation.
    \item Wrote \textbf{Introduction and Significance} section.
    \item Plotted all graphs and charts in \textbf{Comparative Study and Discussion}.
    \item Helped group move forward by making technical decisions, distributing works, setting up deadlines, and facilitating coordination between groupmates.
\end{itemize}

@@

\ilc{FGSM} is a \textit{white-box} evasion attack algorithm. Being \text{white-box} means the attacker is assumed to have access to the internal of the model: the structure, the parameters... basically each and every details of the model is considered to be known.

In this case, we mostly care about the \ilc{loss} function of the model. The intuition of \ilc{FGSM} is elegent and effective -- in short: gradient ascent. Assume we have an benign example $x$ with label $y$, and we are trying to make it adversarial by letting the model classify $x_{\text{adv}}$ to be not $y$. We apply the following pertubation on $x$ to achieve an $x_{\text{adv}}$

\begin{equation}
    x_{\text{adv}} = x + \epsilon \cdot \textit{sign}(\nabla_x J(\theta, x, y))
\end{equation}

where $J$ is the \ilc{loss} function and $\theta$ is the parameters of the model. It is clearly to tell that by finding a proper amount of $\epsilon$, we know $x_{\text{adv}}$ will eventually cross the $y-\neg y$
